Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
More about screen videos.

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers. The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.

>>>>

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we made a video recording of each participant's computer screen
and simultaneously projected it
into another room with Tor developers.
We recorded what they were saying out loud in their cognitive walk through,
and later added these words to the screen videos as subtitles.
The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening. 
Our talk will feature brief highlights of the screen videos.
